\section{Introduction To CPS}
Cyber-physical systems (CPS) are smart systems that include engineered interacting networks of physical and computational components. Bringing these different components together aims to improve the quality of modern life and introducing the advances of technology to critical areas. The impact of CPS in life can be spotted in many areas, such as; autonomous vehicles, intelligent buildings, smart energy systems, robots, and smart medical devices. 

\subsection{Trustworthiness in CPS}
National Institute of Standards and Technology (NIST) defines trustworthiness of cyber-physical systems as the demonstrable likelihood that the system performs according to designed behaviour under any set of conditions as evidenced by characteristics including, but not limited to, safety, security, privacy, reliability and resilience.

\section{Introduction to security issues in CPS}

\section{Related work}
 
\section{Defining Main comparison parameters}

\section{Results}

\section{Conclusion} 
 
 

\begin{thebibliography}{9}

 
\bibitem{einstein} 
A. H. Land and A. Doig. 
\textit{An automatic method for solving discrete programming problems}. 
Econometrica, 28:497–520, 1960.
 
\bibitem{knuthwebsite} 
 J. D. Little, K. G. Murty, D. W. Sweeney, and C. Karel.
\textit{An algorithm for the travelling salesman problem}. 
Operations Research, 11(6):972–989, 1963.

\bibitem{knuthwebsite} 
 S. Lin and B.W.  Kernighan.
\textit{An effective heuristic algorithm for the travelling salesman problem}.
Operations Research 21 (1973) ,498-516.

\end{thebibliography}
\citep{Doe:2009:Misc}
\cite{Doe:2009:Misc}


